---
title: Forecasts and Highcharts
author: RWW
date: '2019-05-24'
slug: forecasts-and-highcharts
categories:
  - time series
  - R
tags:
  - forecast
  - R
  - R Markdown
  - time series
---

# Beautiful forecasting can be quick and easy

1. I will grab the adjusted closing price of Ford stock (`F`) from January 1, 2018.  
2. Use the `forecast` package to find an ARIMA model and forecast it for 50 periods.  
3. Use `highcharter` to plot it inside a framewidget that is appropriate with the markdown.

```{r CB, warning=FALSE, message=FALSE}
library(tidyquant)
library(forecast)
library(highcharter)
library(widgetframe)
A.Stock <- "F" %>% tq_get(., from = "2018-01-01")
A.Res <- A.Stock %>% select(date, adjusted) 
A.Forecast <- forecast(auto.arima(A.Res$adjusted), level=0.95, n=50)
```

I separated the plot line.  Now to the result.

```{r FW1}
frameWidget(hchart(A.Forecast), width=600)
```

I wonder how easy it is to integrate the stock chart stuff.

```{r SC1}
frameWidget(hchart(A.Stock, type="stock"), width = 600)
```

